Visualising CHD Pathway Inequalities by ethnicity - DRAFT

### 2024-04-23 draft_report.qmd
Add column spanner headings to gt tables

all_gp_reg_pat |>
    pivot_wider(names_from=c(cluster,sex_name),
                names_sep = "_",
                values_from = perc
                )|>
    select(age_group, starts_with("1"), starts_with("2"), starts_with("3"),starts_with("4"),starts_with("5")) |>
  arrange(factor(age_group, 
                 levels = c("<18","18-44","45-64","65-74","75+")))|>
    gt(rowname_col = "age_group")|>
    tab_spanner_delim(delim = "_") |>
    tab_stubhead(label=md("**Age Group**"))|>
    tab_options(heading.title.font.size = 18,
                heading.title.font.weight = "bolder",
                column_labels.font.weight = "bold")|>
    fmt_percent(decimals = 2)|>
    tab_header(title = md("**Table 2** - *Age / Sex Breakdown by Cluster*"))

@@

Table 3 shows that

@@

  gt(rowname_col = "gp_imd_quantile")|>
  tab_stubhead(label=md("**IMD Quantile**"))|>
  tab_options(heading.title.font.size = 18,
              heading.title.font.weight = "bolder",
              column_labels.font.weight = "bold")|>
    tab_stubhead(label=md("**IMD Quantile**"))|>
  fmt_percent(columns=c(starts_with("1"), starts_with("2"), starts_with("3"),starts_with("4"),starts_with("5")),decimals = 2)|>
  tab_header(title = md("**Table 3** - *Index of Multiple Deprivation Breakdown by Cluster*"))
```

patientweighted_practice_imd |>
  mutate(gp_imd_quantile = case_when(gp_imd_decile<=2 ~ 1,
                                     gp_imd_decile==3 ~2,
                                     gp_imd_decile==4 ~2,
                                     gp_imd_decile==5 ~3,
                                     gp_imd_decile==6 ~3,
                                     gp_imd_decile==7 ~4,
                                     gp_imd_decile==8 ~4,
                                     gp_imd_decile>=9 ~5,
                                     .default = 0
  ))|>
  group_by(gp_imd_quantile,cluster)|>
  summarise(patients=sum(patients))|>
  gt()
```

>>>>

all_gp_reg_pat |>
    pivot_wider(names_from=c(cluster,sex_name),
                names_sep = "_",
                values_from = perc
                )|>
    select(age_group, starts_with("1"), starts_with("2"), starts_with("3"),starts_with("4"),starts_with("5")) |>
  arrange(factor(age_group, 
                 levels = c("<18","18-44","45-64","65-74","75+")))|>
    gt(rowname_col = "age_group")|>
    tab_spanner_delim(delim = "_") |>
    tab_spanner(label = "Cluster", columns = c(starts_with("1"), starts_with("2"), starts_with("3"),starts_with("4"),starts_with("5")))|>
    tab_stubhead(label=md("**Age Group**"))|>
    tab_options(heading.title.font.size = 18,
                heading.title.font.weight = "bolder",
                column_labels.font.weight = "bold")|>
    fmt_percent(decimals = 2)|>
    tab_header(title = md("**Table 2** - *Age / Sex Breakdown by Cluster*"))

@@

Table 3 shows that the most diverse cluster has the greatest proportion of patients in practices in the most deprived quantile. Cluster 2 has the greatest proportion of patients in practices in the least deprived quantile.

@@

  gt(rowname_col = "gp_imd_quantile")|>
  tab_stubhead(label=md("**IMD Quantile**"))|>
  tab_options(heading.title.font.size = 18,
              heading.title.font.weight = "bolder",
              column_labels.font.weight = "bold")|>
    tab_stubhead(label=md("**IMD Quantile**"))|>
  tab_spanner(label = "Cluster", columns = c(starts_with("1"), starts_with("2"), starts_with("3"),starts_with("4"),starts_with("5")))|>
  fmt_percent(columns=c(starts_with("1"), starts_with("2"), starts_with("3"),starts_with("4"),starts_with("5")),decimals = 2)|>
  tab_header(title = md("**Table 3** - *Index of Multiple Deprivation Breakdown by Cluster*"))
```
